\bf Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-07-16 manuscript/main.tex
widetilde H

	\subsection{Step 1: Computing smoothed PLS components}  \label{subsec: Step 1: Computing Smoothed PLS components}
	This representation allows us to work with coefficient vectors, simplifying notation. Section~\ref{sec: pls component computation intermediate} outlines the core strategy for computing the PLS components in this reduced space. Building on this, we then introduce our regularized and smoothed estimation procedure, which constitutes the first step of the iterative algorithm.

	\subsubsection{Core strategy for PLS component direction estimation}\label{sec: pls component computation intermediate}
Building on the basis function approximation in Section~\ref{sec: finite basis approximation}, we now present the core strategy for directly estimating the hybrid PLS component direction. 
This stretagey fully leverages both the continuous nature of the functional components and the function-scalar hybrid structure, and can be implemented via simple matrix-vector multiplications. Building on this strategy, Section \ref{sec: Regularization of PLS Components} presents the estimation procedure for our suggest method.

We describe the strategy at the $l$-th iteration. For simplicity, we omit the iteration index and assume the observations have been residualized from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for details). The  PLS component direction is estimated by the unit-norm direction $\xi \in \tilde{\mathcal{H}}$ that maximizes the squared empirical covariance, which quantifies the linear dependence between the PLS scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$, defined as

\begin{equation}\label{def:squared_empirical_cov}
	 	\widehat{\textnormal{Cov}} 
	 	( \langle 
	 	\widetilde{W},
	 	\xi \rangle_{\mathcal{H}}, Y )
	 	:=
	 	\frac{1}{n} 
	 	\sum_{i=1}^n
	 	y_i
	 	\langle \widetilde{W}_i, \xi \rangle_{\mathcal{H}}
	 	.
	 \end{equation}
We denote the estimated PLS component direction as
	\begin{equation}\label{def:maximizer_squared_empirical_cov}
		\hat{\xi} 
= 
(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1}
)
:= \arg \max_{\xi \in \mathcal{B}^K \times \mathbb{R}^p,
\| \xi  \|_\mathcal{H} = 1
 } \widehat{\textnormal{Cov}}^2 
\bigl(
\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
\bigr),
	\end{equation}
%
	where each functional part $\hat{\xi}_j $  is expanded as
$
		\hat{\xi}_j(t) := 
		\sum_{m=1}^M \hat{\gamma}_{jm} \, b_m(t),
$
and $\hat{\boldsymbol{\xi}}_{K+1}$ is the scalar part. This maximizer can also be represented as a Euclidean vector
\begin{equation}\label{def:maximizer_euclidean_form}
	( \hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top
	\in \mathbb{R}^{MK+p},
\end{equation}
where the coefficient vectors $\hat{\boldsymbol{\gamma}}_1, \ldots, \hat{\boldsymbol{\gamma}}_K$ are defined as in \eqref{def:coef_vector_form}.
Proposition \ref{proposition:eigen_noregul} reformulates  the problem \eqref{def:maximizer_squared_empirical_cov} as  a generalized Rayleigh quotient.
%
\begin{proposition}\label{proposition:eigen_noregul}
Let
$
	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
$
denote the observed data defined in \eqref{def:problem_instance}.
At the $l$-th iteration of the PLS algorithm, the unit-norm maximizer of  the squared empirical covariance defined in \eqref{def:maximizer_squared_empirical_cov}, represented as the Euclidean vector form as in \eqref{def:maximizer_euclidean_form},
is obtained by solving 
\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
	\left(
	\hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
	\right)^\top
	=
	\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
	\quad \text{subject to} \quad \boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi} = 1.
\end{equation}
where
\begin{equation}\label{def:V_matrix}
V := \frac{1}{n^2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)}.
\end{equation}
\end{proposition}
The proof of Proposition \ref{proposition:eigen_noregul}
is provided in Appendix \ref{section:proof:proposition:linear_noregul_system_unregularized}.
Since $V$ is a rank 1, the solution  is  obtained by matrix multiplication and normalization:
	\begin{proposition} \label{proposition:linear_noregul}
	We can compute  $\hat{\boldsymbol{\gamma}}_1, \ldots, \hat{\boldsymbol{\gamma}}_K$ and $\hat{\boldsymbol{\xi}}_{K+1}$ in Proposition \ref{proposition:eigen_noregul} as 
\begin{equation*}
	\hat{\boldsymbol{\gamma}}_j  = \frac{1}{\sqrt{\sum_{j=1}^K 
			\mathbf{y}^\top
			\Theta_j
			B \Theta_j^\top \mathbf{y} 
			+ 
			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
	\Theta_j^\top \mathbf{y},
	\quad
	%%%%%%%%%%%%%%%%
	\hat{\boldsymbol{\xi}}  = \frac{1}{\sqrt{\sum_{j=1}^K 
			\mathbf{y}^\top
			\Theta_j
			B \Theta_j^\top \mathbf{y} 
			+ 
			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
	Z^\top \mathbf{y}.
\end{equation*}
\end{proposition}
The proof of Proposition \ref{proposition:linear_noregul}  is provided in Appendix \ref{section:proof:proposition:linear_noregul}.
The expressions above represent matrix–vector multiplications normalized by a common factor. 
Although the unnormalized coefficients are computed separately for the functional and scalar part of the PLS component direction, the normalization step couples them, allowing the components to influence each other. This enables the procedure to account for the correlation between functional and scalar components.

@@

One possible approach is to extend smoothed functional PCA \citep{Rice1991} to our optimization problem \eqref{def:maximizer_squared_empirical_cov}, leading to the following formulation:
	\begin{equation*}
	\hat{\xi} 
	= 
	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1})
	= \arg \max_{\xi \in \mathcal{B}^K \times \mathbb{R}^p,
		\| \xi  \|_\mathcal{H} = 1
	} 
	\biggl\{
	\widehat{\textnormal{Cov}}^2 
	\bigl(
	\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
	\bigr)
	- \sum \limits_{j=1}^K \lambda_j 
	\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
	\biggr\}
	,
\end{equation*}
where the smoothing parameters $\{\lambda_j\}_{j=1}^K$ control the trade-off between maximizing covariance and penalizing roughness. Here, the penalization term can be written in matrix form as:
		\begin{align*}
	\sum \limits_{j=1}^K 
	\lambda_j
	\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
&=
	\sum \limits_{j=1}^K 
\lambda_j
\int_0^1 \bigl\{ \sum_{l=1}^M \theta_{ijl} \, b_l^{\prime \prime}(t) \bigr\}^2 dt
\\&	 =
%%%%%%%%%%%%%%%%%%%
	\sum \limits_{j=1}^K 
\lambda_j
\sum_{l=1}^M
\sum_{m=1}^M
\theta_{ijl} \theta_{ijm}
\int_0^1
 \, b_l^{\prime \prime}(t) 
  b_m^{\prime \prime}(t)
  dt
\\&	 =
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sum \limits_{j=1}^K
\lambda_j
\boldsymbol{\gamma}_j^\top
B^{\prime \prime} 
\boldsymbol{\gamma}_j
%%%%%%%%%%%%%%%%%%%%%%%%%%
\\&= 
\boldsymbol{\xi}^{\top} \Lambda \mathbb{B}^{\prime \prime} \boldsymbol{\xi},
\end{align*}
where we recall that $\mathbb{B}^{\prime \prime} $ is defined in \eqref{def:gram_block}, 
	where $\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ is defined as
\begin{equation}\label{def:Lambda}
	\Lambda = \mathrm{blkdiag}(\lambda_1 I_M, \cdots, \lambda_K I_M, 0_{p \times p}) , 
\end{equation}
$0_{p \times p}$ denotes a $p \times p$ matrix with all elements equal to zero.

However, the above approach assumes that the functional predictors admit an orthogonal expansion in the $L^2$ sense. As an alternative, we adopt the strategy of \citet{Silverman1996}, which works under weaker conditions than those required by \citet{Rice1991}. This is achieved by replacing the standard orthonormality constraint with one based on a modified inner product that accounts for roughness. Building on this idea, the following proposition reformulates the hybrid PLS problem as a generalized Rayleigh quotient, yielding a smoothed PLS direction that maximizes the squared covariance over a class of smooth functions.

\begin{proposition}\label{proposition:eigen_noregul}
	Let
	$
	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
	$
	denote the observed data defined in \eqref{def:problem_instance}.
	At the $l$-th iteration of the PLS algorithm, let
	$( \hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top$
	denote the coefficients of $\hat{\xi}$, defined in \eqref{def:maximizer_squared_empirical_cov},
	which corresponds to the projected unit-norm direction that maximizes the squared empirical covariance.
	These coefficients are obtained by solving the following generalized eigenvalue problem:
	\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
		\left(
		\hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
		\right)^\top
		=
		\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
		\quad \text{subject to} \quad \boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi} = 1,
	\end{equation}
	where
	\begin{equation}\label{def:V_matrix}
		V := \frac{1}{n^2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)},
	\end{equation}

@@

	\begin{proposition} \label{Proposition: Regularized generalized rayleigh quotient}
		At each $l$-th iteration of the first step of the PLS algorithm involving the residualized response and predictors $Y_i \equiv Y_i^{[l]}$ and $\mathbf{W}_i \equiv \mathbf{W}_i^{[l]}$, consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$. Recall from \eqref{def:V_star} that  $V^\ast$ is defined as
		\begin{equation*}
			\mathbf{V}^\ast = n^{-2}\begin{bmatrix}
				J \widetilde{C}^\top \mathbf{y}\mathbf{y}^\top \widetilde{C} J & J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z} \\
				\mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J &   \mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z}
			\end{bmatrix} = n^{-2} J^\ast \widetilde{C}^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C}^{*} J^\ast
			\in \mathbb{R}^{(MK+p) \times (MK+p)}.
		\end{equation*}
		and  $\xi^*=(\mathbf{a}^{\top}, \boldsymbol{\theta}^{\top})^\top \in \mathbb{R}^{MK + p}$. Then, the $l$-th smoothed PLS component, $\widehat{\xi} \equiv \widehat{\xi}_l$ can be obtained in the following way.
		We first compute the basis coefficients by solving the optimization problem
		Note that the penalty term can be written concisely using matrices as:
		\begin{equation}
			\textnormal{PEN} \left( \hat{\xi}_j \right) 
			=  \int_0^1 
			\bigl\{ \hat{\xi}_j^{''}(t) \bigr\}^2 dt = \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)},
			\label{eq: roughness penalty}
		\end{equation}
		where the last term is obtained using the basis expansion $\psi^{(k)}(t)=\mathbf{a}^{(k)T}\mathbf{b}^{(k)}(t)$.

		\begin{align}
			\begin{split}
				&\arg \max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \; \frac{\xi^{*\top} \mathbf{V}^\ast \xi^*}{\xi^{*\top}(J^\ast+\Lambda \ddot{J}^\ast) \xi^*} , \quad \textit{or equivalently}, \\ 
				&\arg \max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1.
				\label{eq: Regularized generalized rayleigh quotient equation}
			\end{split}
		\end{align}
		We then express the smoothed component in terms of the basis functions as
		\begin{equation*}
			\widehat{\xi}[\mathbf{t}] = [\widehat{\psi}(\mathbf{t})^\top, \widehat{\boldsymbol{\theta}}^\top]^\top =  \mathbb{B}[\mathbf{t}]^\top \widehat{\xi}^\ast.   
		\end{equation*}
		The $l$-th PLS score $\widehat{\rho}_{i} \equiv \widehat{\rho}_{il}$ can be obtained as 
		\begin{equation}\label{compute_pls_score}
			\widehat{\rho}_i = \langle \mathbf{W}_i, \widehat{\xi} \rangle_\mathcal{H}
		\end{equation}
	\end{proposition}
	The proof of Proposition \ref{Proposition: Regularized generalized rayleigh quotient} is provided in Appendix \ref{section:proof:eigenproblem_derivation}.
	Here, $\lambda_k$ $(k=1, \ldots, K)$ is a positive smoothing parameter that controls the trade-off between the goodness of fit and the amount of smoothness in $\psi^{(k)}$. Smaller $\lambda_k$ produces PLS components that fit more closely to the observed data, but selecting too small value may cause overfitting. The estimated PLS component reverts back to the unregularized version of Proposition \ref{proposition:eigen_noregul} when $\lambda_k=0$ for all $k$. On the other hand, larger $\lambda_k$ places more emphasis on smoothing $\psi^{(k)}$. In the limit $\lambda_k \rightarrow \infty$, each of the functions is forced to be of the form $\psi^{(k)}(t)=a+bt$ for some constants $a$ and $b$. In practice, $\{\lambda_k\}_{k=1}^K$ as well as the number of PLS components $L$ to be estimated can be chosen by cross-validation based on a certain predictive performance criterion (e.g., mean squared error).

>>>>

	\subsection{Step 1: Computing smoothed PLS component direction}  \label{subsec: Step 1: Computing Smoothed PLS components} 
We begin with the first step of the iterative algorithm: estimating the smooth PLS component direction. Section~\ref{sec: pls component computation intermediate} introduces the core optimization problem for this step, formulated as a generalized Rayleigh quotient. Building on this, Section~\ref{sec: Regularization of PLS Components} presents a modified version that promotes smoothness, which is the estimation procedure for our proposed method, along with a efficient computation scheme.

	\subsubsection{Core optimization problem for PLS component direction estimation}\label{sec: pls component computation intermediate}
Building on the basis function approximation in Section~\ref{sec: finite basis approximation}, we now present the core optimization problem that directly estimates the hybrid PLS component direction. This strategy fully leverages the continuous nature of the functional components and the function-scalar hybrid structure, and can be implemented using simple matrix-vector multiplications.

We describe the strategy at the $l$-th iteration. For simplicity, we omit the iteration index and assume the observations have been residualized from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for details). The  PLS component direction is estimated by the unit-norm direction $\xi \in \widetilde{\mathcal{H}}$ that maximizes the squared empirical covariance, which quantifies the linear dependence between the PLS scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$, defined as

\begin{equation}\label{def:squared_empirical_cov}
	 	\widehat{\textnormal{Cov}} 
	 	( \langle 
	 	\widetilde{W},
	 	\xi \rangle_{\mathcal{H}}, Y )
	 	:=
	 	\frac{1}{n} 
	 	\sum_{i=1}^n
	 	y_i
	 	\langle \widetilde{W}_i, \xi \rangle_{\mathcal{H}}
	 	.
	 \end{equation}
We denote the estimated PLS component direction as
	\begin{equation}\label{def:maximizer_squared_empirical_cov}
		\hat{\xi} 
= 
(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1}
)
:= \arg \max_{\xi \in \widetilde{\mathcal{H}}
 }~\widehat{\textnormal{Cov}}^2 
\bigl(
\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
\bigr)~s.t.~\| \xi  \|_\mathcal{H} = 1,
	\end{equation}
%
	where each functional part $\hat{\xi}_j $  is expanded as
$
		\hat{\xi}_j(t) := 
		\sum_{m=1}^M \hat{\gamma}_{jm} \, b_m(t),
$
and $\hat{\boldsymbol{\xi}}_{K+1}$ is the scalar part. This maximizer can also be represented as a Euclidean vector
\begin{equation}\label{def:maximizer_euclidean_form}
	( \hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top
	\in \mathbb{R}^{MK+p},
\end{equation}
where the coefficient vectors $\hat{\boldsymbol{\gamma}}_1, \ldots, \hat{\boldsymbol{\gamma}}_K$ are defined as in \eqref{def:coef_vector_form}.
Proposition \ref{proposition:eigen_noregul} reformulates  the problem \eqref{def:maximizer_squared_empirical_cov} as  a generalized Rayleigh quotient.
%
\begin{proposition}\label{proposition:eigen_noregul}
Let
$
	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
$
denote the observed data defined in \eqref{def:problem_instance}.
At the $l$-th iteration of the PLS algorithm, the unit-norm maximizer of  the squared empirical covariance defined in \eqref{def:maximizer_squared_empirical_cov}, represented as the Euclidean vector form as in \eqref{def:maximizer_euclidean_form},
is obtained by solving 
\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
	\left(
	\hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
	\right)^\top
	=
	\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
	\quad \text{subject to} \quad \boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi} = 1.
\end{equation}
where
\begin{equation}\label{def:V_matrix}
V := \frac{1}{n^2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)}.
\end{equation}
\end{proposition}
The proof of Proposition \ref{proposition:eigen_noregul}
is provided in Appendix \ref{section:proof:proposition:linear_noregul_system_unregularized}.
Since $V$ is a rank 1, the solution  is  obtained by matrix multiplication and normalization:
	\begin{proposition} \label{proposition:linear_noregul}
	We can compute  $\hat{\boldsymbol{\gamma}}_1, \ldots, \hat{\boldsymbol{\gamma}}_K$ and $\hat{\boldsymbol{\xi}}_{K+1}$ in Proposition \ref{proposition:eigen_noregul} as 
\begin{equation*}
	\hat{\boldsymbol{\gamma}}_j  = \frac{1}{\sqrt{\sum_{j=1}^K 
			\mathbf{y}^\top
			\Theta_j
			B \Theta_j^\top \mathbf{y} 
			+ 
			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
	\Theta_j^\top \mathbf{y},
	\quad
	%%%%%%%%%%%%%%%%
	\hat{\boldsymbol{\xi}}  = \frac{1}{\sqrt{\sum_{j=1}^K 
			\mathbf{y}^\top
			\Theta_j
			B \Theta_j^\top \mathbf{y} 
			+ 
			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
	Z^\top \mathbf{y}.
\end{equation*}
\end{proposition}
The proof of Proposition \ref{proposition:linear_noregul}  is provided in Appendix \ref{section:proof:proposition:linear_noregul}.
The expressions above represent matrix–vector multiplications normalized by a common factor. 
Although the unnormalized coefficients are computed separately for the functional and scalar part of the PLS component direction, the normalization step couples them, allowing the components to influence each other. This enables the procedure to account for the correlation between functional and scalar components.

@@

One possible approach is to extend smoothed functional PCA \citep{Rice1991} to our optimization problem \eqref{def:maximizer_squared_empirical_cov}, leading to the following formulation:
	\begin{equation*}
	\hat{\xi} 
	= 
	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1})
	= \arg \max_{\xi \in \mathcal{B}^K \times \mathbb{R}^p,
		\| \xi  \|_\mathcal{H} = 1
	} 
	\biggl\{
	\widehat{\textnormal{Cov}}^2 
	\bigl(
	\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
	\bigr)
	- \sum \limits_{j=1}^K \lambda_j 
	\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
	\biggr\}
	,
\end{equation*}
where the smoothing parameters $\{\lambda_j\}_{j=1}^K$ control the trade-off between maximizing covariance and penalizing roughness. Here, the penalization term can be written in matrix form as:
		\begin{align*}
	\sum \limits_{j=1}^K 
	\lambda_j
	\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
&=
	\sum \limits_{j=1}^K 
\lambda_j
\int_0^1 \bigl\{ \sum_{l=1}^M \theta_{ijl} \, b_l^{\prime \prime}(t) \bigr\}^2 dt
\\&	 =
%%%%%%%%%%%%%%%%%%%
	\sum \limits_{j=1}^K 
\lambda_j
\sum_{l=1}^M
\sum_{m=1}^M
\theta_{ijl} \theta_{ijm}
\int_0^1
 \, b_l^{\prime \prime}(t) 
  b_m^{\prime \prime}(t)
  dt
\\&	 =
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sum \limits_{j=1}^K
\lambda_j
\boldsymbol{\gamma}_j^\top
B^{\prime \prime} 
\boldsymbol{\gamma}_j
%%%%%%%%%%%%%%%%%%%%%%%%%%
\\&= 
\boldsymbol{\xi}^{\top} \Lambda \mathbb{B}^{\prime \prime} \boldsymbol{\xi},
\end{align*}
where $\boldsymbol{\xi}$ is the concatenated coefficient vector form of $\xi$ as defined in \eqref{def:maximizer_euclidean_form}, $\mathbb{B}^{\prime\prime}$ is defined in \eqref{def:gram_block}, and $\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ is given by
\begin{equation}\label{def:Lambda}
	\Lambda := \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p}),
\end{equation}
where $0_{p \times p}$ denotes the $p \times p$ zero matrix.

However, the approach of \citet{Rice1991} assumes that the functional predictors admit an orthogonal expansion in the $L^2$ sense. As an alternative, we adopt the strategy of \citet{Silverman1996}, which replaces the standard orthonormality constraint with a weaker one based on a modified inner product that incorporates roughness.
Building on this idea, Proposition \ref{proposition:eigen_regul} modifies the optimization problem presented in Proposition \ref{proposition:eigen_noregul}, yielding a smoothed PLS direction that maximizes the squared covariance over a class of smooth functions.

\begin{proposition}\label{proposition:eigen_regul}
	Let
	$
	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
	$
	denote the observed data defined in \eqref{def:problem_instance}.
	At the $l$-th iteration of the PLS algorithm, let
	$( \hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top$
	denote the coefficients of $\hat{\xi}$, defined in \eqref{def:maximizer_squared_empirical_cov},
	which corresponds to the projected unit-norm direction that maximizes the squared empirical covariance.
	These coefficients are obtained by solving the following generalized eigenvalue problem:
	\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
		\left(
		\hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
		\right)^\top
		=
		\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
		\quad \text{subject to} \quad \boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi} = 1,
	\end{equation}
	where
	\begin{equation}\label{def:V_matrix}
		V := \frac{1}{n^2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)},
	\end{equation}

@@

	\begin{proposition} 
		At each $l$-th iteration of the first step of the PLS algorithm involving the residualized response and predictors $Y_i \equiv Y_i^{[l]}$ and $\mathbf{W}_i \equiv \mathbf{W}_i^{[l]}$, consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$. Recall from \eqref{def:V_star} that  $V^\ast$ is defined as
		\begin{equation*}
			\mathbf{V}^\ast = n^{-2}\begin{bmatrix}
				J \widetilde{C}^\top \mathbf{y}\mathbf{y}^\top \widetilde{C} J & J \widetilde{C}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z} \\
				\mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C} J &   \mathbf{Z}^\top \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \mathbf{Z}
			\end{bmatrix} = n^{-2} J^\ast \widetilde{C}^{*\top} \widetilde{\mathbf{y}} \widetilde{\mathbf{y}}^\top \widetilde{C}^{*} J^\ast
			\in \mathbb{R}^{(MK+p) \times (MK+p)}.
		\end{equation*}
		and  $\xi^*=(\mathbf{a}^{\top}, \boldsymbol{\theta}^{\top})^\top \in \mathbb{R}^{MK + p}$. Then, the $l$-th smoothed PLS component, $\widehat{\xi} \equiv \widehat{\xi}_l$ can be obtained in the following way.
		We first compute the basis coefficients by solving the optimization problem
		Note that the penalty term can be written concisely using matrices as:
		\begin{equation}
			\textnormal{PEN} \left( \hat{\xi}_j \right) 
			=  \int_0^1 
			\bigl\{ \hat{\xi}_j^{''}(t) \bigr\}^2 dt = \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)},
			\label{eq: roughness penalty}
		\end{equation}
		where the last term is obtained using the basis expansion $\psi^{(k)}(t)=\mathbf{a}^{(k)T}\mathbf{b}^{(k)}(t)$.

		\begin{align}
			\begin{split}
				&\arg \max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \; \frac{\xi^{*\top} \mathbf{V}^\ast \xi^*}{\xi^{*\top}(J^\ast+\Lambda \ddot{J}^\ast) \xi^*} , \quad \textit{or equivalently}, \\ 
				&\arg \max \limits_{\xi^* \in \mathbb{R}^{MK+p}} \;  \xi^{*\top} \mathbf{V}^\ast \xi^* \quad \textnormal{subject to}  \quad \xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1.
				\label{eq: Regularized generalized rayleigh quotient equation}
			\end{split}
		\end{align}
		We then express the smoothed component in terms of the basis functions as
		\begin{equation*}
			\widehat{\xi}[\mathbf{t}] = [\widehat{\psi}(\mathbf{t})^\top, \widehat{\boldsymbol{\theta}}^\top]^\top =  \mathbb{B}[\mathbf{t}]^\top \widehat{\xi}^\ast.   
		\end{equation*}
		The $l$-th PLS score $\widehat{\rho}_{i} \equiv \widehat{\rho}_{il}$ can be obtained as 
		\begin{equation}\label{compute_pls_score}
			\widehat{\rho}_i = \langle \mathbf{W}_i, \widehat{\xi} \rangle_\mathcal{H}
		\end{equation}
	\end{proposition}
	The proof of Proposition \ref{proposition:eigen_regul} is provided in Appendix \ref{section:proof:eigenproblem_derivation}.
	Here, $\lambda_k$ $(k=1, \ldots, K)$ is a positive smoothing parameter that controls the trade-off between the goodness of fit and the amount of smoothness in $\psi^{(k)}$. Smaller $\lambda_k$ produces PLS components that fit more closely to the observed data, but selecting too small value may cause overfitting. The estimated PLS component reverts back to the unregularized version of Proposition \ref{proposition:eigen_noregul} when $\lambda_k=0$ for all $k$. On the other hand, larger $\lambda_k$ places more emphasis on smoothing $\psi^{(k)}$. In the limit $\lambda_k \rightarrow \infty$, each of the functions is forced to be of the form $\psi^{(k)}(t)=a+bt$ for some constants $a$ and $b$. In practice, $\{\lambda_k\}_{k=1}^K$ as well as the number of PLS components $L$ to be estimated can be chosen by cross-validation based on a certain predictive performance criterion (e.g., mean squared error).
